%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[margin, 10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above

\setlength{\textwidth}{5.1in} % Text width of the document

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------

\moveleft.5\hoffset\centerline{\large\bf Jake Gockley} % Your name at the top
 
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'
 
\moveleft.5\hoffset\centerline{84 Nash Street} % Your address
\moveleft.5\hoffset\centerline{New Haven, CT 06511}
\moveleft.5\hoffset\centerline{\textit{Email:} Jake.Gockley@Yale.edu  \textit{Mobile:} (802) 373-4890}


%----------------------------------------------------------------------------------------

\begin{resume}

%----------------------------------------------------------------------------------------
%	OBJECTIVE SECTION
%----------------------------------------------------------------------------------------
 
%\section{OBJECTIVE}  

%A position in the field of computers with special interests in business applications programming, information processing, and management systems. 

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{EDUCATION}

{\sl Doctor of Philosophy PhD,} Genetics \\
Yale University, New Haven, CT, 2017 \textit{Exp}\\
Focus: High-throughput Enhancer Functionalization Assay Development 

{\sl Masters of Science M.S,} Genetics \\
Yale University, New Haven, CT, 2014 \\
Focus: Multifactorial Neuropsychiatric Disease  

{\sl Bachelor of Science B.S,} Biological Science, GPA: 3.66 \\
University of Vermont, Burlington, VT, 2009 \\
Concentration: Genetics, Biochemistry \\
Minor: Chemistry \\
Thesis: The Folate Receptor in Paramecium

%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{COMPUTER \\ SKILLS} 

{\sl Languages:} 
Perl, Python, R, C++, HTML, LaTex. \\
{\sl Specific Skills:} Statistical analysis and visualization of big data.\\
{\sl Software:} Evernote, Serial Cloner, XCode, SPSS, Microsoft: Word, Excel, \& PowerPoint, Adobe Illustrator \& Photoshop.\\  
{\sl Operating Systems:} Windows, Apple ios, Unix. 

%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{LANGUAGES} 
{\sl Fluent:} English; {\sl Proficient:} Spanish \& Portuguese 

\begin{itemize} \itemsep -2pt % Reduce space between items
\item 1 month full immersion in Cuernavaca, Mexico.  
\item Attended Escola Graduada de Sao Paulo, 2 years.
\end{itemize}
%----------------------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
 
\section{EXPERIENCE}

{\sl Manager, Public Relations/Publicity, \& Permittee} \hfill 2012-Present \\
Gryphon's Pub, Graduate \& Professional Student Center at Yale, New Haven, CT 

\begin{itemize} \itemsep -2pt % Reduce space between items
\item Responsible for liquor permit, insurance, hiring, daily operations, website redesign, \& building maintenance/upgrades of a \$700,000/year business.    
\item Assisted with event planning/coordination, and accounting. 
\end{itemize}
 
{\sl Lab Research Technician} \hfill 2009-2011 \\
University of Vermont, Burlington, VT 
\begin{itemize} 
\item Responsible for lab management as well as independent and team lead projects.
\end{itemize} 

{\sl Assistant Brewer} \hfill 2007-2008 \\
American Flatbread, Burlington, VT
\begin{itemize}
\item Aseptic production and transfer of 500 gallon batches. 
\end{itemize} 

%{\sl Independent Research Project} \hfill 2007-2008 \\
%University of Vermont, Burlington, VT
%\begin{itemize}
%\item Thesis: The Folate Receptor in Paramecium 
%\end{itemize} 

{\sl Laboratory Assistant} \hfill 2006-2007 \\
University of Vermont, Burlington, VT
\begin{itemize}
\item Prepared culture medium, ran gels, genotyped weekly mouse samples. 
\end{itemize} 

{\sl Ice Maintenance and Zamboni Driver} \hfill 2005-2006 \\
University of Vermont, Burlington, VT
\begin{itemize}
\item Carried out daily operations on shift and night ice maintenance. 
\end{itemize} 

%----------------------------------------------------------------------------------------
%	Publications
%----------------------------------------------------------------------------------------

\section{PUBLICATIONS} 
Emera D, Yin J, Reilly SK, \textbf{Gockley J}, Noonan JP. "{\sl Origin and evolution of developmental enhancers in
the mammalian neocortex}" PNAS, In Review.

\textbf{Gockley J}, Willsey AJ, Dong S, Dougherty JD, Constantino JN, Sanders SJ. "{\sl The female protective effect in autism spectrum disorder is not mediated by a single genetic locus.}" Molecular Autism, 2015.

Dong S, Walker MF, Carriero NJ, DiCola M, Willsey AJ, Ye AY, Waqar Z, Gonzalez LE, Overton JD, Frahm S, Keaney JF, Teran NA, Dea J, Mandell JD, Hus Bal V, Sullivan CA, DiLullo NM, Khalil RO, \textbf{Gockley J}, Yuksel Z, Sertel SM, Ercan-Sencicek AG, Gupta AR, Mane SM, Sheldon M, Brooks AI, Roeder K, Devlin B, State MW, Wei L, Sanders SJ. "{\sl De novo insertions and deletions of predominantly paternal origin are associated with autism spectrum disorder}" Cell Reports, 2014.

Willsey AJ, Sanders SJ, Li M, Dong S, Tebbenkamp AT, Muhle RA, Reilly SK, Lin L, Fertuzinhos S, Miller JA, Murtha MT, Bichsel C, Niu W, Cotney J, Ercan-Sencicek AG, \textbf{Gockley J}, Gupta AR, Han W, He X, Hoffman EJ, Klei L, Lei J, Liu W, Liu L, Lu C, Xu X, Zhu Y, Mane SM, Lein ES, Wei L, Noonan JP, Roeder K, Devlin B, Sestan N, State MW. "{\sl Coexpression networks implicate human midfetal deep cortical projection neurons in the pathogenesis of autism.}" Cell, 2014.

%----------------------------------------------------------------------------------------
%	Awards & Honors
%----------------------------------------------------------------------------------------

\section{AWARDS \& HONORS} 

{\sl \textbf{Dean's List}, 7 semesters} \hfill 2005-2009 \\
{\sl \textbf{Beta Beta Beta} Biology Honors Society} \hfill 2007-2009 \\
{\sl \textbf{APLE Award}, Research Grant} \hfill 2008


%----------------------------------------------------------------------------------------
%	COMMUNITY SERVICE SECTION
%---------------------------------------------------------------------------------------- 

\section{COMMUNITY \\ SERVICE}

{\sl \textbf{Beta Phi}, Non-profit public health initiative} \hfill 2009-2011
\begin{itemize}
\item Organized and administered public survey across the Greater Boston Area and presented findings to MBTA officials. 
\end{itemize} 

%----------------------------------------------------------------------------------------
%	Laboratory Techniques 
%---------------------------------------------------------------------------------------- 

\section{LABORATORY TECHNIQUES}

{\sl \textbf{Bench Techniques:} Recombinant DNA, Bacterial transformation, Mammalian cell transfection, Bacterial \& Mammalian RNA/DNA isolation, cDNA synthesis, PCR, qPCR, Genomic shotgun library construction, Genomic \& transcriptomic Hi-Seq library preparation, Mammalian sub-culture, Western blotting, Massively parallel enhancer assays (MPRA), STARR-Seq, Luciferase enhancer activity assays, Emulsion PCR, Radiographic and florescent based enzyme kinetics, PAGE oligo purification, Surface plasmon resonance.}

{\sl \textbf{Data Analysis:} Whole genome sequencing, RNA-Seq, ChIP-Seq, Genotyping array data, integration of genotyping data sets (specifically AGRE and SSC Autism cohorts) with phenotypic measures and functional genomic data, Bayesian Inference, UCSC track-hub construction, Multi-dimensional scaling, permutation testing.}

%----------------------------------------------------------------------------------------
%	References
%---------------------------------------------------------------------------------------- 

%\section{REFERENCES}



%----------------------------------------------------------------------------------------
%	EXTRA-CURRICULAR ACTIVITIES SECTION
%----------------------------------------------------------------------------------------

%\section{EXTRA-CURRICULAR \\ ACTIVITIES} 

%Elected {\it House Manager}, Rho Phi Sorority \\
%Elected {\it Sports Chairman} \\
%Attended Krannet Leadership Conference \\
%Headed delegation to Rho Phi Congress \\
%Junior varsity basketball team \\
%Participant, seven intramural athletic teams 

%----------------------------------------------------------------------------------------

\end{resume}
\end{document}